From noise to knowledge: how randomness generates novel phenomena and reveals information

### 2018-03-07 paper/paper.Rmd
submitted revisions

abstract: |
  # Article Type: Review & Synthesis
  # Running title: From noise to knowledge
  # Figures: 4
  # Tables: 0
  # Word count: 7430
  # Word count in abstract: 181
  # Number of References: 117
  # Archive statement:

>>>>

abstract: |
  # Article Type: Review & Synthesis
  # Running title: From noise to knowledge
  # Figures: 4
  # Tables: 0
  # Word count: 7430
  # Word count in abstract: 181
  # Number of References: 111
  # Archive statement:
